A Quantitative Genetic Linked Selection Model of Linked Selection in Humans

### 2023-07-25 manuscript/manuscript.tex
data dryad

We would like to thank Nate Pope and Rasmus Nielsen for helpful advice, and
Martin Kircher for providing special CADD tracks. This research was supported
by NIH awards R35GM148253 and R01HG010774 to ADK

@@

All code from \texttt{bgspy} and our Jupyter Lab \parencite{Kluyver_undated-ol}
notebooks for analysis are available on GitHub
(\url{https://github.com/vsbuffalo/bprime}). The main model fits are available
as Python Pickle objects on FigShare (XXX).

>>>>

We would like to thank Graham McVicker, Priya Moorjani, Rasmus Nielsen, Nate
Pope, Guy Sella, and Peter Sudmant for helpful advice, and Martin Kircher for
providing modified CADD tracks. This research was supported by NIH awards
R35GM148253 and R01HG010774 to ADK

@@

All code from \texttt{bgspy} and our Jupyter Lab \parencite{Kluyver_undated-ol}
notebooks for analysis are available on GitHub
(\url{https://github.com/vsbuffalo/bprime}). The main model fits are available
as Python Pickle objects on Data Dryad
(\url{https://doi.org/10.5061/dryad.qnk98sfnv}).
